---
output:
  md_document:
    variant: markdown_github
---

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

[![img](https://img.shields.io/badge/Lifecycle-Experimental-339999)](https://github.com/bcgov/repomountie/blob/master/doc/lifecycle-badges.md)

# bcsapps

This package was developed to simplify shiny app development at BCStats. It uses `r bcgovr::create_bcgov_project()` to set up an RProject with all the files necessary to comply with bcgov standards and then also adds in the files needed for a basic BCStats shiny app.

Using this package for initializing shiny apps will also ensure consistency across BCStats' apps

### Features

#### Functions

`r create_bcstats_app()` Create a new shiny web application project with folders and files to meet both the bcgov standards (utilizing [bcgovr](https://github.com/bcgov/bcgovr)) and the BCStats standards for shiny apps.


#### Modules

`r bcsHeaderUI()` and `r bcsHeaderServer()` Add the standard BCStats header to your app. An appname is required in `r bcsHeaderUI()` for the title to be included in the header. To exclude the drop down list of links to other BCStats apps (kept up to date in [bcstatslinks](https://github.com/bcgov/bcstatslinks)), use `r bcsHeaderServer(links = FALSE)` the default is `r TRUE`.

`r bcsFooterUI()` and `r bcsFooterServer` Add the standard BCStats footer to your app.

Note that `r create_bcstats_app()` generates a basic app.R file with these modules already included.

### Installation

This package relies on the bcstatslinks package, so that needs to be installed first. To install packages from github, use the remotes package

```{r}

install.packages("remotes")
remotes::install_github("bcgov/bcstatslinks")
remotes::install_github("bcgov/bcsapps")

library(bcsapps)
```


### Usage

Use this package in combination with the [bcgovr](https://github.com/bcgov/bcgovr) package. 

1. To start, open RStudio and ensure the working directory is the folder you wish to set up the RProject in (Alternately, you can provide a path to `create_bcstats_app()`)
2. Run `create_bcstats_app(coc_email = "<insert email address to be used in the code of conduct file>")`
3. Run `bcgovr::use_bcgov_git(coc_email = "<insert email address to be used in the code of conduct file>")` to initialize git version control
4. Run `bcgovr::use_bcgov_github(coc_email = "<insert email address to be used in the code of conduct file>")` to open a bcgov GitHub repository

Note, to avoid typing in your email several times it is recommended to add an option to your `r .Rprofile`. You can easily edit your `r .Rprofile` with `r usethis::edit_r_profile()` and then add in the line options("bcgovr.coc.email" = "your.email@gov.bc.ca". This will edit (and create if necessary) the  `r .Rprofile` file under C:/Users/<username>. If you have settings in `r .Rprofile` on C:/Program Files/R/ they will continue to be used at startup as well. 

Once your github project is initialized, add in the citz and bcstats topics by clicking the settings "gear" icon next to About on the right panel on GitHub.

To change the name of your "master" branch to "main":

1. Go to Settings -> Branches on GitHub and edit the name of your default branch
2. In RStudio click Pull on the Git tab to pull in the new branch
3. Click on the drop down that says "master" and switch to the branch (REMOTE:ORIGIN) main


### Project Status

Experimental

### Getting Help or Reporting an Issue

To report bugs/issues/feature requests, please file an [issue](https://github.com/bcgov/bcsapps/issues/).

### How to Contribute

If you would like to contribute to the package, please see our 
[CONTRIBUTING](CONTRIBUTING.md) guidelines.

Please note that this project is released with a [Contributor Code of Conduct](CODE_OF_CONDUCT.md). By participating in this project you agree to abide by its terms.

### License

```
Copyright 2021 Province of British Columbia

Licensed under the Apache License, Version 2.0 (the &quot;License&quot;);
you may not use this file except in compliance with the License.
You may obtain a copy of the License at

http://www.apache.org/licenses/LICENSE-2.0

Unless required by applicable law or agreed to in writing, software distributed under the License is distributed on an &quot;AS IS&quot; BASIS,
WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND, either express or implied.
See the License for the specific language governing permissions and limitations under the License.
```

---
*This project was created using the [bcgovr](https://github.com/bcgov/bcgovr) package.* 
